---
title: "Tidy Analysis of MLB Batted Balls"
author: "Joshua Albert"
format: html

---

## Loading Data
```{r}
#| message: false

#| code-fold: false

library(tidyverse)
library(tidymodels)
library(skimr)
library(kableExtra)
``` 

## Read in Data
```{r}
park_dimensions <- read.csv("https://raw.githubusercontent.com/agmath/agmath.github.io/refs/heads/master/data/classification/park_dimensions.csv")


batted_balls <- read.csv("https://raw.githubusercontent.com/agmath/agmath.github.io/refs/heads/master/data/classification/battedballs.csv")

```

## Joinig Data
```{r}
batted_balls <- batted_balls %>%
left_join(park_dimensions, by = c("park" = "park"))


```

We joined the `batted_balls` and `parks` data together, to obtain a full data set with `r nrow(batted_balls)` rows and `r ncol(batted_balls)` columns

```{r}
batted_balls%>%
  skim()

```


Split into training and test data

```{r}
set.seed(434)
data_splits <- initial_split(batted_balls, 0.85, strata = is_home_run)

train <- training(data_splits)
test <- testing(data_splits)


```

## Exploratory Data Analysis

How and why do home runs happen?

Filtering Rows

```{r}
train %>% 
  filter(is_home_run == 1) 
 
train %>%
  filter(launch_angle > 45)

train%>%
  filter(str_detect(NAME, "Fenway"))
```
Selecting just a few columns

```{r}
train %>%
  select(launch_speed, launch_angle, is_home_run)
```
Building new variables from old ones (*Feature Engineering*)

```{r}
train %>%
  mutate(fast_pitch = ifelse(pitch_mph > 100, "yes", "no"))

```


### Summary Statistics

Home runs...

```{r}
train %>%
  count(is_home_run)%>%
  mutate(prop = 100*n/sum(n))

```


```{r}
train %>%
  summarize(pct_hr = 100*mean(is_home_run))
```


```{r}

```




Summarizing Launch Angle

```{r}
train %>%
  filter(!is.na(launch_angle)) %>%
  summarize(
    min_angle = min(launch_angle),
    mean_angle = mean(launch_angle),
    median_angle = median(launch_angle),
    max_angle = max(launch_angle),
    sd_angle = sd(launch_angle),
    
  )
```



#### Grouped Summaries

```{r}
train %>%
  group_by(is_home_run, NAME) %>%
  filter(!is.na(launch_angle)) %>%
  summarize(
    min_angle = min(launch_angle),
    mean_angle = mean(launch_angle),
    median_angle = median(launch_angle),
    max_angle = max(launch_angle),
    sd_angle = sd(launch_angle),
  ) 

    
```

### Data Viz


```{r}

train %>%
  ggplot() + 
  geom_bar(aes(x = is_home_run)) +
  labs(
    title = "Homeruns"
  )


```

```{r}

train %>%
  ggplot() + 
  geom_histogram(aes(x = pitch_mph, y = after_stat(density))) +
geom_density(aes(x = pitch_mph))



```
```{r}
train %>%
   ggplot() +
geom_bar(aes(x = bb_type, fill = bearing)) +
  labs(
    title = "Distribution of Direction Hit and Type of Hit"

  )

```

